% !TEX encoding = UTF-8
% !TEX program = pdflatex
% !TEX spellcheck = en_GB
% !BIB TS-program = biber

\documentclass[english,a4paper, nologo]{europasscv}
\usepackage[english]{babel}

\usepackage[backend=biber,autolang=hyphen,sorting=none,style=numeric,maxbibnames=99,doi=false,isbn=false,maxcitenames=2]{biblatex}
\usepackage{csquotes}
\usepackage{europasscv-bibliography}
\bibliography{europasscv_example}
% in the bibliography, mark all occurrences in bold:
\ecvbibhighlight{Wang}{Youchao}{}

%\ecvbibhighlightsecond{Wang}{Youchao}{}

	\ecvname{Youchao Wang}
	\ecvaddress{Department of Engineering, University of Cambridge}
	\ecvmobile{+44 7936 674795}
	\ecvemail{yw479@cam.ac.uk}

% \ecvpicture[width=3.8cm]{picture.jpg}

% \date{}

\begin{document}
  \begin{europasscv}

  \ecvpersonalinfo
%  \ecvbigitem{Job applied for}{European project manager}

  \vspace*{-1cm}
  \ecvsection{Education}

\ecvtitlelevel{Oct 2019 -- Present}{Ph.D. in Engineering}{University of Cambridge}
\ecvitem{}{Electrical Engineering Division, Department of Engineering}
\vspace*{-0.4cm}

\ecvtitlelevel{Oct 2018 -- Oct 2019}{M.Phil. in Engineering}{University of Cambridge}
\ecvitem{}{Electrical Engineering Division, Department of Engineering}
\vspace*{-0.4cm}

\ecvtitlelevel{Sep 2016 -- Jun 2018}{B.Eng. in Electronic Engineering}{University of Manchester}
\ecvitem{}{First class honours. GPA top 1\%. Second year direct entry.}
\vspace*{-0.4cm}

\ecvtitlelevel{Sep 2014 -- Jun 2018}{B.Eng. in Electrical Engineering}{North China Electric Power University, Beijing}
\ecvitem{}{Joint 2+2 programme with University of Manchester.}
\vspace*{-0.3cm}
  \ecvsection{Work experience}
%  \vspace*{-0.2cm}
  \ecvtitlelevel{Jan 2021 -- Jul 2021}{Internship}{Huawei Technologies Sweden \& UK}
  \ecvitem{}{Research on the theory and simulation of Fourier optics based optical processor.}
  \vspace*{-0.4cm}
  
  \ecvtitlelevel{Jan 2020 -- Present}{Undergraduate Supervision Tutor}{St. John’s College, University of Cambridge}
  \ecvitem{}{Give individual supervision courses to second-year Engineering students at St John’s College.}
  \ecvitem{}{Course Part IB Paper 6, including Linear Systems and Control, Communications, Fourier Transforms \& Signal and Data Analysis.}
    \vspace*{-0.4cm}
    
  \ecvtitlelevel{Jan 2019 -- Mar 2019}{Part Time Research Assistant}{Department of Engineering, University of Cambridge}
	\ecvitem{}{Embedded system circuit design and embedded system software development.}
%  \ecvitem{}{\ecvhighlight{Business or sector}\quad European institution}
   \vspace*{-0.4cm}
   
  \ecvtitlelevel{Aug 2018 -- Sep 2018}{Research Assistant}{Department of Engineering, University of Cambridge}
  \ecvitem{}{Research topic: Deriving physically-inspired sensor signal invariants using a physics specification language.}
   \vspace*{-0.4cm}
   
  \ecvtitlelevel{Jul 2017 -- Sep 2017}{Research Assistant}{School of Electrical and Electronic Engineering, University of Manchester}
  \ecvitem{}{Research topic: “Internet of Things” LoRaWAN sensor system for protecting rivers and watercourses}
  
\vspace*{-0.3cm}
    	\ecvsection{Project Portfolio}
  \ecvtitle{Nov 2020 -- Present}{Raspberry PI Cluster System for Computer Generated Holography}
  \ecvitem{}{Supporting and leading a M.Res. student on a multi-node cluster system hologram generation project.}
  \ecvitem{}{Focus: Distributed computing, Computer generated holography, Embedded systems, Optimization.}
  \vspace*{-0.2cm}
  
  
  \ecvtitle{Oct 2019 -- Present}{Opto-electronic Neural Network Processor for Deep Learning Applications}
  \ecvitem{}{Ph.D. Degree Research Project, Supervisor: Prof. Timothy Wilkinson}
  \ecvitem{}{Focus: Optical information processing, Fourier optics, Spatial light modulator, Machine learning algorithms, FPGA, Hardware and software co-design.}
  \vspace*{-0.2cm}
  
  \ecvtitle{Mar 2019 -- Present}{Spatial Light Modulator Driver Platform for Holographic Displays}
  \ecvitem{}{Research Project, Supervisor: Prof. Timothy Wilkinson}
  \ecvitem{}{Focus: Spatial light modulator display driver, Holography, PCB hardware design, FPGA implementation. Designed a bespoke multi-layer high-speed PCB and implemented customized FPGA firmware.}
  \vspace*{-0.2cm}
  
  \ecvtitle{Mar 2019 -- Oct 2019}{Computer Generated Holography on a Digital Signal Processor System}
  \ecvitem{}{M.Phil. Degree Research Project, Supervisor: Prof. Timothy Wilkinson}
  \ecvitem{}{Focus: Computer generated holograms, Digital signal processing, Algorithm implementation. Implemented multiple CGH algorithms within a high-end TI DSP processor board.}
  \vspace*{-0.2cm}
  
  \ecvtitle{Aug 2018 -- Mar 2019}{Sensor Data Fusion using Automated Dimensional Function Synthesis}
  \ecvitem{}{M.Phil. Degree Research Project, Supervisor: Dr. Phillip Stanley-Marbell}
  \ecvitem{}{Focus: Miniature hardware system design, Firmware implementation, Physics specification language compiler design. Key contributor to the construction of \textit{Newton} computer language compiler for dimensional analysis.}
  \vspace*{-0.2cm}
  
  \ecvtitle{Jun 2017 -- May 2018}{IoT Water Quality Monitoring System for Protecting Watercourses}
  \ecvitem{}{Research Project, Supervisors: Prof. Bruce Grieve and Prof. Christopher Collins}
  \ecvitem{}{Focus: Low-cost turbidity sensor design, Low power embedded system design, LoRaWAN system.}
  \ecvitem{}{Developed a bespoke PCB board with multiple sensors and maintained the server communication.}
  
\vspace*{-0.3cm}
  \ecvsection{Selected Honours}
  \vspace*{-0.2cm}
  	\ecvtitlelevel{}{\small{CSC Cambridge-Trust Scholarship (Fully-funded Ph.D.)}}{Jun. 2019}
  	\vspace*{-0.5cm}
  	\ecvtitlelevel{}{\small{CSC Masters Programme Scholarship (Partially-funded M.Phil.)}}{Jun. 2018}
  	\vspace*{-0.5cm}
  	\ecvtitlelevel{}{\small{Third Year 3\textsuperscript{rd} Prize in School of EEE, UoM (Top 3 of the year)}}{Jun. 2018}
  	\vspace*{-0.5cm}
  	\ecvtitlelevel{}{\small{2018 Beijing Outstanding Higher Education Graduate Title}}{Jun. 2018}
  	\vspace*{-0.5cm}
  	\ecvtitlelevel{}{\small{Second Year 1\textsuperscript{st} Prize in School of EEE, UoM (Top 1)}}{Oct. 2017}
  	\vspace*{-0.5cm}
  	\ecvtitlelevel{}{\small{Beijing Capital University \& College ``Pioneer Cup'' Outstanding Member Title}}{Oct. 2016}
  	\vspace*{-0.5cm}
  	\ecvtitlelevel{}{\small{Entrepreneur Student Scholarship (Top 3) at NCEPU}}{Dec. 2015}
  	\vspace*{-0.5cm}
	\ecvtitlelevel{}{\small{1\textsuperscript{st} Prize (Top 2) Student Scholarship at NCEPU}}{Sep. 2015}
	\vspace*{-0.5cm}
	\ecvtitlelevel{}{\small{Special Award (Top 1‰) in National English Competition for College Students}}{May. 2015}
	\vspace*{-0.5cm}
	\ecvtitlelevel{}{\small{2\textsuperscript{nd} prize (Top 10) in 20\textsuperscript{th} National English Speaking Competition, Beijing region}}{Dec. 2014}

\ecvsection{Position of Responsibility}
\vspace*{-0.2cm}
\ecvtitlelevel{}{\small{Reviewer of \textit{Applied Optics}}}{2020 -- Present}
\vspace*{-0.5cm}
\ecvtitlelevel{}{\small{Vice-president of Cambridge Chinese Students and Scholars Association}}{2020 -- Present}
\vspace*{-0.5cm}
\ecvtitlelevel{}{\small{Second and Third Year School of EEE Student Representative, UoM}}{2016 -- 2018}
\vspace*{-0.5cm}
\ecvtitlelevel{}{\small{Chairman of NCEPU International Education School Students’ Union}}{2015 -- 2016}
\vspace*{-0.5cm}
\ecvtitlelevel{}{\small{Chairman of Tsinghua High School Students’ Union}}{2012 -- 2013}
\vspace*{-0.5cm}
\ecvtitlelevel{}{\small{Chairman and General Secretary of Tsinghua High School Model United Nations}}{2012 -- 2013}

\nopagebreak
  
  \ecvsection{Personal information}


  \vspace*{-0.2cm}
  \ecvblueitem{Subject related skills}{\begin{ecvitemize}
  		\item \ecvhighlight{Software Programming: }Proficient in C programming (Embedded C and compiler design). Know well in C++, Python (Tensorflow Framework), Java (Eclipse IDE), Matlab and Simulink.
  		\item \ecvhighlight{Hardware programming:} Know well in Verilog and VHDL. Experience in HLS arithmetic C and Xilinx Vitis.
  		\item \ecvhighlight{Hardware development:} Proficient in Altium Designer. Know well in Eagle, Designspark and NI Multisim (Circuit and PCB design). Know well in Solidworks and Fusion360 (Product design).
  		\item \ecvhighlight{Environment:} Proficient in MplabX IDE and Code Composer Studio. Know well in Cadence Software (VLSI), Xilinx IDE and Quartus Prime (FPGA).
  		\item \ecvhighlight{Embedded systems: }Proficient in the use of microcontrollers (ARM family, PIC family). Know well TI KeyStone DSPs and Lattice iCE40 FPGAs.  Experience in Raspberry Pi and Beagle Bone Boards.	
  	\end{ecvitemize}  
  }
  \vspace*{-0.4cm}
	
	\ecvblueitem{IT}{
	\begin{ecvitemize}
	\item 	Proficient in MacOS and Linux (Ubuntu, Debian, etc.).
	\item 	Proficient in the use of \LaTeX \ (Invited talk How to use \LaTeX \ at University of Cambridge, 2019).
	\item	Proficient in the use of Adobe Family (After Effect, Audition, Premiere, Photoshop and Illustrator), Microsoft Office Products, Corel VideoStudio, Edius and FinalCut Pro.
	\item	Proficient in photography, filmmaking and video editing. 
	\item	Experience in web development and server maintenance.
	\end{ecvitemize}	
}
\vspace*{-0.4cm}
	\ecvblueitem{Language}{English (IELTS 8.0/9.0), Chinese (Native Speaker)}
   \vspace*{-0.4cm}

  \ecvblueitem{Driving licence}{Full clean driving licences in China and UK.}
  

\pagebreak

	\nocite{*}
	\renewcommand{\section}[2]{\ecvsection{#2}}
	\printbibtabular[title=Publications]

	\ecvblueitem{\cite{DaomingDong2020} \cite{Dong:20}}{Corresponding author.}	
  
  \end{europasscv}

\end{document}
