\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[blue]{banking}                  % optional argument are 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

%\newcommand*{\gitlabsocialsymbol}  {{\small\faGitlab}~} % <=============

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
\usepackage{enumitem}
\usepackage{lmodern}


% adjust the page margins
%old - still looks good if want one more line
%\usepackage[top=1.1cm, bottom=1.2cm, left=2cm, right=2cm]{geometry}
%current
\usepackage[top=2.0cm, bottom=2cm, left=1.8cm, right=1.8cm]{geometry}
%\setlength{\hintscolumnwidth}{3cm}    					% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% Hyperlinks
\definecolor{linkcolour}{rgb}{0,0.2,0.6}			% hyperlinks setup
\AfterPreamble{\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=gray,pdfnewwindow=true}}

% Can redefine the symbols between the details - here redefine bullet points to three spaces
%\renewcommand*{\maketitlesymbol}{~~~}

% Which color do we want for the alternate colouring on right side of page
%\colorlet{altColor}{color1} % Choose this one for blue
\colorlet{altColor}{color2} % Choose this one for grey
\colorlet{normal}{color0} % Change back to black afterwards

% personal data
\name{Youchao}{Wang}
%\title{ResumÃ© title}                               % optional, remove / comment the line if not wanted
\address{Department of Engineering, University of Cambridge}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty

\phone[mobile]{+44 793 667 4795}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
%\phone[fixed]{+2~(345)~678~901}
%\phone[fax]{+3~(456)~789~012}
\email{yw479@cam.ac.uk}                      % optional, remove / comment the line if not wanted
%\homepage{www.andrewkadis.com} %Commented out as used above instead                          % optional, remove / comment the line if not wanted
\social[linkedin][www.linkedin.com/in/youchao-wang-8b806175/]{Youchao Wang} %Commented out as used above instead                         % optional, remove / comment the line if not wanted
%\social[twitter]{jdoe}                             % optional, remove / comment the line if not wanted
\social[github][github.com/Siegfriedchao]{Siegfriedchao} 
\social[gitlab][gitlab.com/Siegfriedchao]{Siegfriedchao} 
                            % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted

%the photo will show when \moderncvtheme[blue]{banking} is set to {mondern}
%\photo[64pt][0.4pt]{picture.png}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother


% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}


%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}

\maketitle

\vspace*{-1.8cm}

\section{Education}

%\gitlabsocialsymbol
\vspace*{-0.00cm}

\cventry{}{\vspace*{-0.6cm}}{Ph.D. in Engineering}{\textnormal{\em \small\color{altColor} University of Cambridge, UK, 2019 -- present\color{normal}}}{}{
	\begin{itemize}[topsep=0.0mm, itemsep=1.0mm, leftmargin=7.0mm]
		\item Electrical Engineering Division, Department of Engineering.
	\end{itemize}
}

\cventry{}{\vspace*{-0.6cm}}{M.Phil. in Engineering (By Research)}{\textnormal{\em \small\color{altColor} University of Cambridge, UK, 2018 -- 2019\color{normal}}}{}{
	\begin{itemize}[topsep=0.0mm, itemsep=1.0mm, leftmargin=7.0mm]
		\item Electrical Engineering Division, Department of Engineering.
	\end{itemize}
}

\cventry{}{\vspace*{-0.6cm}}{B.Eng. Electronic Engineering (1\textsuperscript{st} Class Honours)}{\textnormal{\em \small\color{altColor} University of Manchester, UK, 2016 -- 2018\color{normal}}}{}{
	\begin{itemize}[topsep=0.0mm, itemsep=1.0mm, leftmargin=7.0mm]
		\item Second year direct entry. Final grade: 87\%. Third year rank: 3/250. Second year rank: 1/240.
	\end{itemize}
}

\cventry{}{\vspace*{-0.6cm}}{B.Eng. Electrical Engineering and its Automation}{\textnormal{\em \small\color{altColor} North China Electric Power University, China, 2014 -- 2018\color{normal}}}{}{
	\begin{itemize}[topsep=0.0mm, itemsep=1.0mm, leftmargin=7.0mm]
		\item  First and Second year final result: 83\%. First year rank: 2/119.
	\end{itemize}
}


\cventry{}{\vspace*{-0.6cm}}{High School Graduate}{\textnormal{\em \small\color{altColor} Tsinghua High School, China, 2011 -- 2014\color{normal}}}{}{
%	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
%		\item  Software Engineering, Computer Architecture, Data Structures \& Algorithms, Object-Oriented Design
%	\end{itemize}
}

\vspace*{-0.8cm}

\section{Project Portfolio}

\vspace*{0.0cm}

\vspace*{-0.0cm}
\cventry{}{}{Hybrid opto-electronic neural network processor for deep learning applications}{\textnormal{\em \small\color{altColor}2019 -- \textit{present} \color{normal}}}{}{
	\vspace*{-0.6cm}
	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
		\item Ph.D. Degree Research Project, Supervisor: Prof. Timothy Wilkinson
		\item Focus: Optical information processing, Fourier optics, Spatial light modulator, Machine learning algorithms, FPGA, Hardware and software co-design.
	\end{itemize}
}

\vspace*{-0.0cm}
\cventry{}{}{Interfacing a High Speed Ferroelectric Spatial Light Modulator}{\textnormal{\em \small\color{altColor}2019 -- present \color{normal}}}{}{
	\vspace*{-0.6cm}
	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
		\item Research Side-Project, Supervisor: Prof. Timothy Wilkinson
		\item Focus: Spatial light modulator display driver, Computer generated holograms, PCB hardware design, FPGA firmware implementation.
	\end{itemize}
}

\vspace*{-0.0cm}
\cventry{}{}{Computer Generated Holography on a Digital Signal Processor System}{\textnormal{\em \small\color{altColor}2019 \color{normal}}}{}{
	\vspace*{-0.6cm}
	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
		\item M.Phil. Degree Research Project, Supervisor: Prof. Timothy Wilkinson
		\item Focus: Computer generated holograms, Digital signal processing, Algorithm implementation.
		\item Published a first-author conference paper focusing on the implementation of a fast hologram generation algorithm on a multi-core digital signal processor.
	\end{itemize}
}

\vspace*{-0.0cm}
\cventry{}{}{Sensor Data Fusion using Automated Dimensional Function Synthesis}{\textnormal{\em \small\color{altColor}2018 -- 2019 \color{normal}}}{}{
\vspace*{-0.6cm}
\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
\item M.Phil. Degree Research Project, Supervisor: Dr. Phillip Stanley-Marbell
\item Focus: Miniature hardware system design, Firmware implementation, Physics specification language compiler design.
\item Published a first-author conference and journal double-track paper focusing on the implementation of a dimensional function synthesis compiler.
\end{itemize}
}

\vspace*{-0.0cm}
\cventry{}{}{``IoT'' Water Quality Monitoring System for Protecting Rivers and Watercourses}{\textnormal{\em \small\color{altColor}2017 -- 2018\color{normal}}}{}{
\vspace*{-0.6cm}
\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
\item B.Eng. Degree Individual Project, Supervisor: Prof. Bruce Grieve
\item Focus: Low-cost turbidity sensor design, Low power system design, Encoding and decoding to enhance the data transmission efficiency
\item Published a first-author journal paper focusing on the design of a low-cost turbidity sensor.
\end{itemize}
}

\vspace*{-0.0cm}
\cventry{}{}{Embedded System Project Team Competition (3\textsuperscript{rd} Rank Among 48 Groups)}{\textnormal{\em \small\color{altColor}2016 -- 2017\color{normal}}}{}{
	\vspace*{-0.6cm}
	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
		\item Second-year Team Project: Line-following robotic buggy using light-sensitive sensor array and ultrasound sensor.
		\item A major contributor to hardware design and software implementation, including buggy structural design, line-detection application, motor control and programming.
		\item Leading role in team organisation (team of 4).
		\item 90/100 personal project overall score.
	\end{itemize}
}

\vspace*{-0.4cm}

\section{Work Experience}

\vspace*{-0.0cm}

\cventry{\small\color{altColor} Jan. 2020 -- present}{St. John's College, University of Cambridge, UK\color{normal}}{Undergraduate Supervision Tutor}{}{}{
	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
		\vspace*{-0.1cm}	
		\item Give individual supervision courses to a group of 16 second-year Engineering students at St John's College. 
		\item Course Part IB Paper 6, including Linear Systems and Control, Communications, Fourier Transforms \& Signal and Data Analysis.
	\end{itemize}
}

\cventry{\small\color{altColor} Jan. 2019 -- Mar. 2019}{Department of Engineering, University of Cambridge, UK\color{normal}}{Research Assistant}{}{}{
	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
		\vspace*{-0.1cm}	
		\item Supervisor: Dr. Phillip Stanley-Marbell
		\item Embedded system circuit design and embedded system software development. Part time.
	\end{itemize}
}
%\vspace*{-0.2cm}
\cventry{\small\color{altColor} Aug. 2018 -- Sep. 2018}{Department of Engineering, University of Cambridge, UK\color{normal}}{Research Assistant}{}{}{
	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
		\vspace*{-0.1cm}	
		\item Supervisor: Dr. Phillip Stanley-Marbell
		\item Research topic: Deriving physically-inspired sensor signal invariants using a physics specification language
		\item Compiler Construction, Programming language design, Signal and Noise, Dimensional analysis, Physically-inspired high-level description language (\textit{Newton}).
	\end{itemize}
}
%\vspace*{-0.2cm}

\cventry{\small\color{altColor} Jul. 2017 -- Sep. 2017}{School of Electrical and Electronic Engineering, University of Manchester, UK\color{normal}}{Research Assistant}{}{}{
	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
		\vspace*{-0.1cm}	
		\item Supervisors: Prof. Bruce Grieve in collaboration with Prof. Christopher Collins at University of Reading
		\item Research topic: ``Internet of Things'' LoRaWAN Sensor System for Protecting Rivers and Watercourses
		\item Internet of Things (IoT) in e-Agri, Hardware design, PCB design, Firmware design and implementation, Wireless communication.
	\end{itemize}
}
%\vspace*{-0.2cm}

%\cventry{\small\color{altColor} Jul. 2016 -- Aug. 2016}{Hanban Foreign Learning Programme, North China Electric Power University, China\color{normal}}{Paid personal tutor}{}{}{
%	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
%		\vspace*{-0.1cm}	
%		\item Paid one-on-one tutoring in the form of reading, writing and speaking (Chinese and English).
%	\end{itemize}
%}

\vspace*{-0.4cm}

\section{Position of Responsibility}

\vspace*{0.0cm}


\vspace*{-0.0cm}
\cventry{}{}{Electronic Engineering Third Year Student Representative}{\textnormal{\em \small\color{altColor}2017 -- 2018\color{normal}}}{}{
	\vspace*{-0.60cm}
	%\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
	%\item adsf
	%\end{itemize}
}
\vspace*{-0.7cm}

\vspace*{-0.0cm}
\cventry{}{}{Electrical and Electronic Engineering Second Year Student Representative}{\textnormal{\em \small\color{altColor}2016 -- 2017\color{normal}}}{}{
	\vspace*{-0.60cm}
	%	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
	%	\item adsf
	%	\end{itemize}
}
\vspace*{-0.7cm}

\vspace*{-0.0cm}
\cventry{}{}{Chairman of NCEPU International Education School Students’ Union}{\textnormal{\em \small\color{altColor}2014 -- 2015\color{normal}}}{}{
	\vspace*{-0.60cm}
	%	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
	%		\item adsf
	%	\end{itemize}
}
\vspace*{-0.7cm}

\vspace*{-0.0cm}
\cventry{}{}{Chairman of Tsinghua High School Students’ Union}{\textnormal{\em \small\color{altColor}2012 -- 2013\color{normal}}}{}{
	\vspace*{-0.60cm}
	%	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
	%		\item adsf
	%	\end{itemize}
}
\vspace*{-0.7cm}

\vspace*{-0.0cm}
\cventry{}{}{Chairman and General Secretary of Tsinghua High School Model United Nations}{\textnormal{\em \small\color{altColor}2012 -- 2013\color{normal}}}{}{
	\vspace*{-0.60cm}
	%	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
	%		\item adsf
	%	\end{itemize}
}

\vspace*{-0.8cm}
\vspace*{-0.4cm}

\section{Selected Honours and Awards}

\vspace*{-0.0cm}
\cventry{}{}{CSC Cambridge Scholarship (Fully-funded Ph.D.)}{\textnormal{\em \small\color{altColor}Jun. 2019\color{normal}}}{}{
	\vspace*{-1.1cm}
}

\vspace*{-0.7cm}
\cventry{}{}{CSC Masters Programme Scholarship (Partially-funded M.Phil.)}{\textnormal{\em \small\color{altColor}Jun. 2018\color{normal}}}{}{
	\vspace*{-1.1cm}
}

\vspace*{-0.7cm}
\cventry{}{}{Third Year 3\textsuperscript{rd} Prize in School of EEE, UoM (Top 3 of the year)}{\textnormal{\em \small\color{altColor}Jun. 2018\color{normal}}}{}{
	\vspace*{-1.1cm}
}

\vspace*{-0.7cm}
\cventry{}{}{2018 Beijing Outstanding Higher Education Graduate Title}{\textnormal{\em \small\color{altColor}Jun. 2018\color{normal}}}{}{
	\vspace*{-1.1cm}
}

\vspace*{-0.7cm}
\cventry{}{}{Second Year 1\textsuperscript{st} Prize in School of EEE, UoM (Top 1)}{\textnormal{\em \small\color{altColor}Oct. 2017\color{normal}}}{}{
	\vspace*{-1.1cm}
}

\vspace*{-0.7cm}
\cventry{}{}{Beijing Capital University \& College ``Pioneer Cup'' Outstanding Member Title}{\textnormal{\em \small\color{altColor}Oct. 2016\color{normal}}}{}{
	\vspace*{-1.1cm}
}

\vspace*{-0.7cm}
\cventry{}{}{3\textsuperscript{rd} Prize Student Scholarship at NCEPU}{\textnormal{\em \small\color{altColor}Sep. 2016\color{normal}}}{}{
	\vspace*{-1.1cm}
}

\vspace*{-0.7cm}
\cventry{}{}{Entrepreneur Student Scholarship (Top 3) at NCEPU}{\textnormal{\em \small\color{altColor}Dec. 2015\color{normal}}}{}{
	\vspace*{-1.1cm}
}

\vspace*{-0.7cm}
\cventry{}{}{1\textsuperscript{st} Prize (Top 2) Student Scholarship at NCEPU}{\textnormal{\em \small\color{altColor}Sep. 2015\color{normal}}}{}{
	\vspace*{-1.1cm}
}

\vspace*{-0.7cm}
\cventry{}{}{Special Award (Top 1‰) in National English Competition for College Students}{\textnormal{\em \small\color{altColor} May. 2015\color{normal}}}{}{
	\vspace*{-1.1cm}
}

\vspace*{-0.7cm}
\cventry{}{}{2\textsuperscript{nd} prize (Top 10) in 20\textsuperscript{th} National English Speaking Competition, Beijing region}{\textnormal{\em \small\color{altColor} Dec. 2014\color{normal}}}{}{
	\vspace*{-1.1cm}
}

\vspace*{-1.2cm}

\section{Key Skills}

\vspace*{-0.0cm}
\cventry{}{}{Subject Related}{\textnormal{\em \small\color{altColor}\color{normal}}}{}{
	\vspace*{-0.6cm}
	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
		\item \textbf{Software Programming: }Proficient in C programming (Embedded C and compiler design). Know well in C++, Python (Tensorflow Framework), Java (Eclipse IDE and Android software development), Matlab and Simulink.
		\item \textbf{Hardware programming:} Know well in Verilog and VHDL coding. Experience in HLS arithmetic C and Xilinx Vitis.
		\item \textbf{Hardware development:} Proficient in Altium Designer. Know well in Eagle, Designspark and NI Multisim (Circuit and PCB design). Know well in Solidworks and Fusion360 (Product design).
		\item \textbf{Environment:} Proficient in MplabX IDE and Code Composer Studio. Know well in Cadence Software (VLSI), Xilinx IDE and Quartus Prime (FPGA).
		\item \textbf{Embedded systems: }Proficient in the use of microcontrollers (ARM family, PIC family). Know well TI KeyStone DSPs and Lattice iCE40 FPGAs.  Experience in Raspberry Pi, Beagle Bone Boards.
	\end{itemize}
}

\newpage
\cventry{}{}{IT}{\textnormal{\em \small\color{altColor}\color{normal}}}{}{
	\vspace*{-0.6cm}
	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
		\item Proficient in MacOS and Linux (Ubuntu, Debian, etc.).
		\item Proficient in the use of \LaTeX \ (Invited talk \textit{How to use \LaTeX \ }at University of Cambridge, 2019)
		\item Proficient in the use of Adobe Family (After Effect, Audition, Premiere, Photoshop and Illustrator), Microsoft Office Products, Corel VideoStudio, Edius, FinalCut Pro.
		\item Proficient in Photography, Filmmaking and Video Editing.
	\end{itemize}
}

%\vspace*{-0.2cm}
%\cventry{}{}{Driving Licence}{\textnormal{\em \small\color{altColor}\color{normal}}}{}{
%	\vspace*{-0.6cm}
%	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
%		\item Full clean driving licence in China.
%	\end{itemize}
%}

\vspace*{-0.2cm}
\cventry{}{}{Language}{\textnormal{\em \small\color{altColor}\color{normal}}}{}{
	\vspace*{-0.6cm}
	\begin{itemize}[topsep=0.0mm, itemsep=-1.0mm, leftmargin=7.0mm]
		\item English (\textbf{IELTS 8.0/9.0}), Chinese (Native Speaker)
	\end{itemize}
}

% \vspace*{-0.4cm}
\vspace*{-0.8cm}

\section{Interests}
\vspace*{-0.2cm}
\cvline{}{\small Photography, Tennis, Piano, Model United Nations.}

\vspace*{-0.4cm}

\section{Publication List}
%Setting up a counter so that I don't need to manually change the numbers
\newcounter{counter}
\setcounter{counter}{1}

{\textsc{[\arabic{counter}] A Cost-Optimized Heterogeneous FPGA Architecture for Non-iterative Hologram Generation}}
\newline  Daoming Dong, \textbf{Youchao Wang}, Andrew Kadis and Timothy Wilkinson. \textit{In submission}.

\addtocounter{counter}{1}

{\textsc{[\arabic{counter}] OASys: Envisioning an Opto-electronic Accelerator for Deep Learning Applications}}
\newline  \textbf{Youchao Wang} and Timothy Wilkinson. \textit{In submission}.

\addtocounter{counter}{1}

\textsc{[\arabic{counter}] Computer-Generated Fresnel Holograms Using Field Programmable Gate Arrays}
\newline  Daoming Dong, Andrew Kadis, \textbf{Youchao Wang} and Timothy Wilkinson. In \textit{Proceedings of DH3D}, 2020.

\addtocounter{counter}{1}

\textsc{[\arabic{counter}] HoloBlade: An Open Platform for Holography}
\newline  Andrew Kadis, Daoming Dong, \textbf{Youchao Wang}, Peter Christopher, Ralf Mouthaan and Tim Wilkinson. In \textit{Proceedings of DH3D}, 2020.

\addtocounter{counter}{1}

\textsc{[\arabic{counter}] Holographic Rendering of a Real-World Scene Captured	with a Low-cost RGB-D Camera}
\newline  Fan Yang, \textbf{Youchao Wang}, Ralf Mouthaan and Tim Wilkinson. In \textit{Proceedings of DH3D}, 2020.

\addtocounter{counter}{1}

\href{https://www.spiedigitallibrary.org/journals/Optical-Engineering/volume-59/issue-10/102413/Hardware-implementations-of-computer-generated-holography-a-review/10.1117/1.OE.59.10.102413.full}{\textsc{[\arabic{counter}] Hardware Implementations of Computer Generated Holography: A Review}}
\newline  \textbf{Youchao Wang}, Daoming Dong, Peter Christopher, Andrew Kadis, Ralf Mouthaan, Fan Yang and Timothy Wilkinson. \textit{Optical Engineering}, 59 (10), 102413, 2019.

\addtocounter{counter}{1}

\href{https://ieeexplore.ieee.org/document/8337739}{\textsc{[\arabic{counter}] Predictive Search Algorithm for Phase Holography}}
\newline Peter Christopher, \textbf{Youchao Wang}, and Timothy Wilkinson. \textit{Journal of the Optical Society of America: A}, vol. 36, no. 12, 2019.

\addtocounter{counter}{1}

\textsc{[\arabic{counter}] Computer Hologram Generation With One-Step Phase-Retrieval Using a Digital Signal Processor Board}
\newline  \textbf{Youchao Wang}, Daoming Dong, Peter Christopher, Andrew Kadis and Timothy Wilkinson. In \textit{Proceedings of GlobalSIP 2019}, 2019.

\addtocounter{counter}{1}

\textsc{[\arabic{counter}] Fixed-Point Accuracy Analysis of 2D FFT for the Creation of Computer Generated Hologram}
\newline  Daoming Dong, \textbf{Youchao Wang}, Peter Christopher, Andrew Kadis and Timothy Wilkinson. In \textit{Proceedings of GlobalSIP 2019}, 2019.

\addtocounter{counter}{1}

\href{https://dl.acm.org/citation.cfm?id=3358218}{\textsc{[\arabic{counter}] Deriving Equations from Sensor Data Using Dimensional Function Synthesis}}
\newline  \textbf{Youchao Wang}, Sam Willis, Vasileios Tsoutsouras and Phillip Stanley-Marbell. \textit{ACM Transactions on Embedded Computing Systems}, vol. 18, no. 5, 2019. (\textit{Best Paper Award} at the \textit{2019 ACM/IEEE Embedded Systems Week})

\addtocounter{counter}{1}

\textsc{[\arabic{counter}] Distributed Water Quality Monitoring System using Internet of Things Wireless Protocol – Long Range Wide Area Network}
\newline  Shariar Morshed Rajib, \textbf{Youchao Wang}, Chris Collins and Bruce Grieve. \textit{In Submission}, 2019.

\addtocounter{counter}{1}

\href{https://www.eurosys2019.org/wp-content/uploads/2019/03/eurosys19posters-abstract77.pdf}{\textsc{[\arabic{counter}] Safeguarding Sensor Device Drivers Using Physical Constraints}}
\newline  Gregory Brooks, \textbf{Youchao Wang} and Phillip Stanley-Marbell. In \textit{Proceedings of ACM EuroSys 2019} (poster), Dresden, 2019.

\addtocounter{counter}{1}

\href{https://ieeexplore.ieee.org/document/8337739}{\textsc{[\arabic{counter}] Low-Cost Turbidity Sensor for Low-Power Wireless Monitoring of Fresh-Water Courses}}
\newline  \textbf{Youchao Wang}, Shariar Morshed Rajib, Chris Collins and Bruce Grieve. \textit{IEEE Sensors Journal}, vol. 18, no. 11, 2018. (Officially announced as \textbf{one of the 25 most downloaded} \textit{Sensors Journal} papers in the months of October, November and December 2018, and \textbf{the 7\textsuperscript{th} most popular document} as of January 2019)

\addtocounter{counter}{1}

\href{https://ndnsim.net/2.3/ndnsim-research-papers.html}{\textsc{[\arabic{counter}] Interest Set Mechanism to Improve the Transport of Named Data Networking}}
\newline  Xiaoke Jiang, Jun Bi, \textbf{Youchao Wang} and You Wang. In \textit{Proceedings of ACM SIGCOMM13} (poster, Section 12), Hongkong, 2013. 

\addtocounter{counter}{1}

\href{http://netarchlab.tsinghua.edu.cn/~shock/THU-NetArchLab-ICN-TR-ISTSET-20130517.pdf}{\textsc{[\arabic{counter}] Tech report: Interest Set Mechanism to Improve the Transport of Named Data Networking}}
\newline  Xiaoke Jiang, Jun Bi, \textbf{Youchao Wang} and You Wang.\textit{ Tsinghua University}, 2013. 

\addtocounter{counter}{1}

% \vspace*{-0.1cm}
\vspace*{-0.4cm}

\section{Referees}
\vspace*{-0.2cm}
\cvline{}{Available on request}

\end{document}